GRHL2

### 2018-03-12 ChIP-seq_GRHL2/Manuscript_Figures.Rmd
Added mRNA data

plot(GSE43836[1:2],ylim=c(0,6),type="n", lwd=2, ylab="Read Depth", main="All GRHL2 Sites [GSE43836]")
lines(GSE43836[c(1,5)], lwd=2, col="lightblue")
lines(GSE43836[c(1,6)], lwd=2,  col="pink")
lines(GSE43836[c(1,7)], lwd=2,  col="deeppink")
legend("topright", legend=c("0 min", "45 min", "90 min"),
       col=c("lightblue","pink","deeppink"),pch=20, cex=0.5,horiz = TRUE)

>>>>

plot(GSE43836[1:2],ylim=c(0,6),type="n", lwd=2, ylab="Read Depth", main="Resonsive GRHL2 Sites [GSE43836]")
lines(GSE43836[c(1,5)], lwd=2, col="lightblue")
lines(GSE43836[c(1,6)], lwd=2,  col="pink")
lines(GSE43836[c(1,7)], lwd=2,  col="deeppink")
legend("topright", legend=c("0 min", "45 min", "90 min"),
       col=c("lightblue","pink","deeppink"),pch=20, cex=0.5,horiz = TRUE)
